Blame and Coercion: Together Again for the Second Time

### 2019-10-03 paper.tex
cite GitHub issue on TBC vs COE
hyper coercion theorems

\newtheorem{theorem}{Theorem}[section]
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^l & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}

@@

Last year, \citet{kuhlenschmidt2018efficient} present Grift, a space-efficient 
and blame-tracking compiler for a gradually typed language of the same name. 
This implementation is based on the $ Lazy D $ Coercion Calculus.
Their result suggests that implementing coercion is practical. And this is the 
first time product types is considered. Their treatment to products in 
coercions, however, is shown incorrect. **

\todo[inline]{kc: ** I want to cite the GitHub issue page here.}

@@

@@

\subsection{Hyper-coercion is Correct}

\begin{theorem}[Hyper-coercion bi-simulates cast]	
	$ t \Downarrow_B o $ if and only if $ t \Downarrow_H o $
\end{theorem}

\subsection{Hyper-coercion is Space-efficient}

>>>>

\newtheorem{theorem}{Theorem}[]
\newtheorem{proposition}{Proposition}[]
\newtheorem{corollary}{Corollary}[]
\newcommand{\figref}[1]{Fig.~\ref{#1}}
\newcommand{\stxrule}[3]{#1 & ::= & #3 & \text{#2}\\}
\newcommand{\stxrulecont}[1]{& | & #1 & \\}
\newcommand{\funrule}[3]{#1 & = & #2 & #3\\}
\newcommand{\comprule}[4]{#1 & \fatsemi^l & #2 & = & #3 & #4 \\}
\newcommand{\plus}[0]{+}
\newcommand{\judgetype}[3]{#1 \vdash #2 : #3}

@@

Last year, \citet{kuhlenschmidt2018efficient} present Grift, a space-efficient 
and blame-tracking compiler for a gradually typed language of the same name. 
This implementation is based on the $ Lazy D $ Coercion Calculus.
Their result suggests that implementing coercion is practical. And this is the 
first time product types is considered. Their treatment to products in 
coercions, however, is shown incorrect (\citet{Gradual-TypingType-based-casts}).

@@

\begin{theorem}[$ Lazy D $ Hyper-coercion is a proper cast representation]
	\  \\
\begin{enumerate}
	\item If $ v : T $, then $ id(T) \; v = \mathtt{succ} \; v $
	\item If $ v : T_1 $,
	$ c_1 $ is a hyper-coercion from $ T_1 $ to $ T_2 $, and 
	$ c_2 $ is from $ T_2 $ to $ T_3 $,\\
	then $ seq(c_1,c_2) \; v = (c_1 \; v) >>= c_2 $
	\item If $ v : T_1 $ and $ \neg T_1 \smile T_2 $,
	then $ cast(T_1, l, T_2) \; v = \mathtt{fail} \; l $
	\item If $ v : \star $, 
	then $ cast(\star,l,\star) \; v = \mathtt{succ} \; v $
	\item If $ v : P $,
	then $ cast(\star,l,Q) \; (inj \; P \; v) = cast(P,l,Q) \; v $
	\item If $ v : P $,
	then $ cast(P,l,\star) \; v = \mathtt{succ} \; (inj \; P \; v) $
	\item If $ v : \iota $,
	then $ cast(\iota,l,\iota) \; v = \mathtt{succ} \; v $
	\item $ cast(S_1 \rightarrow T_1,l,S_2 \rightarrow T_2) \; (fun \; c_1 \; 
	E \; b \; c_2) $ \\
	$ = \mathtt{succ} \; fun \; seq(cast(S_2,l,S_1),c_1) \; E \; b 
	\; seq(c_2,cast(T_1,l,T_2)) $ 
	\item $ cast(S_1 \times T_1,l,S_2 \times T_2) \; (cons \; v_1 \; c_1 \; 
	v_2 \; c_2) $ \\
	$ = \mathtt{succ} \; (cons \; v_1 \; seq(c_1,cast(S_1,l,S_2)) \; v_2 \; 
	seq(c_2,cast(T_1,l,T_2))) $ 
	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inl \; v \; c) = 
	\mathtt{succ} \; (inl \; v \; seq(c,cast(S_1,l,T_1)) ) $ 
	\item $ cast(S_1 \plus T_1,l,S_2 \plus T_2) \; (inr \; v \; c) = 
	\mathtt{succ} \; (inr \; v \; seq(c,cast(S_2,l,T_2)) ) $ 
\end{enumerate}
\end{theorem}

\begin{proposition}[Every proper cast represenation is correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $
	\[
	e \Downarrow_{B}^{D} o \; \text{if and only if} \; 
	e \Downarrow_{C}^{D} o
 	\]
\end{proposition}

\begin{corollary}[$ Lazy D $ hyper-coercion is correct]
	If $ \judgetype{\emptyset}{e}{T} $ and $ o : T $
	\[
	e \Downarrow^{D}_{B} o \; \text{if and only if} \; 
	e \Downarrow^{D}_{H} o
	\]
\end{corollary}

@@
